---
title: "Application Exercise 2 - Air Quality Data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries, echo=FALSE}

library(readr)
library(ggplot2)
library(dplyr)
library(DT)

```

This exercise is part of workshops, undergraduate and graduate courses taught by the Global Health Engineering Group at ETH Zurich. 



# Data

```{r}

dat_link <- "https://raw.githubusercontent.com/Global-Health-Engineering/manuscript-hospital-air-quality/main/data/intermediate/malawi-hospitals-air-quality.csv"

dat_in <- read_csv(data_link)

# Create a vector of hospital locations

vec_hospital_name <- dat_in %>% 
  count(location) %>% 
  pull(location)

```

The data used in this exercise comes from a study implemented by [@Authors_Manuscript__Malawi_2021]. Air quality data (PM2.5 and PM10) was collected in roughly 5-minute intervals from eight locations at one hospital over the period of 3 months. The locations are `r knitr::combine_words(vec_hospital_name)`.

