---
title: "Application Exercise 2 - Air Quality Data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries, echo=FALSE}

library(readr)
library(ggplot2)
library(dplyr)
library(DT)

```

This exercise is part of workshops, and undergraduate and graduate courses taught by the Global Health Engineering Group at ETH Zurich. 

# Data

```{r}

# This code stores a link to the CSV resource on github as an Object named 'dat_link'
# It does that using the so called assignment operator <- (keyboard shortcut: Alt + -)
# After running the code, the name shows up in the Environment pane in the top right of window 
# It means that you can re-use it in another location

dat_link <- "https://raw.githubusercontent.com/Global-Health-Engineering/manuscript-hospital-air-quality/main/data/intermediate/malawi-hospitals-air-quality.csv"

# This code uses a function named 'read_csv()' to read the data that is stored in the object dat_link
# The data is then stored in a new object named 'dat_in' 
# After running the code, the name shows up in the Environment pane in the top right of window 

dat_in <- read_csv(dat_link)

# This code will create a vector (we will worry about what that is another time)
# The vector contains the values that sit in the variable location 
# We will also worry about the %>% another time

vec_hospital_name <- dat_in %>% 
  count(location) %>% 
  pull(location)

```

The data used in this exercise comes from a study implemented by researchers of the Global Health Engineering Group. The data is published openly on GitHub (Authors, 2021). Air quality data (PM2.5 and PM10) was collected in roughly 5-minute intervals from eight locations at one hospital in Malawi over the period of 3 months. The locations are `r knitr::combine_words(vec_hospital_name)`.

# Data transformation




# References

Authors, A. O., Kalina, M., Tilley, E., & Schöbitz, L. (2021). Manuscript - Malawi Hospital Air Quality Data - Notebook (Version 0.0.1) [Computer software]. https://github.com/Global-Health-Engineering/manuscript-hospital-air-quality


